Compositional Certified Resource Bounds

### 2015-04-15 paper/main.tex
some updates to the caption

\renewcommand{\max}[0]{{\rm mx}}
\nocaptionrule \caption{
  Comparison of the bounds generated by KoAT, Rank,
  LOOPUS, SPEED, and our tool $\toolname$ on several
  challenging linear examples. Results for KoAT and SPEED were extracted
  from previous publications~\cite{GulwaniJK09,GulwaniMC09,GulwaniZ10,SinnZV14} because KoAT cannot take C programs as
  input in its current version and SPEED is not available.
  Entries marked with ? indicate that we cannot test the respective example with the tool. Entries
  marked with --- indicate that the tool failed to produce a result. We write
  $\max(a,b)$ for the maximum of $a$ and $b$.  Functions with names of the form \code{tXX} are complex tests
  that we designed during the development of $\toolname$.  The source code for all the functions
  is available in the extended version~\cite{anon_extended}.
}
\vspace{6pt}
\label{tab:eval}
\footnotesize

>>>>

\renewcommand{\max}[0]{{\rm mx}}
\nocaptionrule \caption{
  Comparison of the bounds generated by KoAT, Rank,
  LOOPUS, SPEED, and our tool $\toolname$ on several
  challenging linear examples. Results for KoAT and SPEED were extracted
  from previous publications~\cite{GulwaniJK09,GulwaniMC09,GulwaniZ10,SinnZV14} because KoAT cannot take C programs as
  input in its current version and SPEED is not available.
  Entries marked with ? indicate that we cannot test the respective example with the tool. Entries
  marked with --- indicate that the tool failed to produce a result. We write
  $\max(a,b)$ for the maximum of $a$ and $b$.  Functions with names of the form \code{tXX} are challenging tests
  that we designed during the development of $\toolname$.  The source code for all functions
  is available in the extended version~\cite{anon_extended}.
}
\vspace{6pt}
\label{tab:eval}
\footnotesize
